---
title: "week10-pdfgen"
author: "Jin Chen"
date: "8/3/2020"
output: pdf_document
---

```{r message=FALSE, warning=FALSE, echo=FALSE}
#Libraries
library(tidyverse)
```

# Data Import and Cleaning
In this block I imported the National Ongitudinal Study of Adolescent to Adult Health Wave IV, 2008 dataset from the UNC Dataverse website. I selected three variables and convereted gender to a factor variable.

```{r message=FALSE}
health_tbl <- read_tsv("../data/w4inhome_dvn.tab") %>% 
  select(attractiveness = H4MH8,
         pregnancies = H4TR9,
         gender = BIO_SEX4) %>% 
  mutate(gender = factor(gender, levels = c(1,2), labels = c("Male", "Female")))
```

# Analysis
In this block I conducted a multiple linear regression of pregnancies on the two independent variables attractiveness and gender, checked assumptions and exmained a coefficients table. 

```{r message=FALSE}
model <- lm(pregnancies ~ attractiveness * gender, data = health_tbl) #The specification first*second indicates the cross of first and second. This is the same as first + second + first:second.
plot(model)
summary(model)
```
Attractiveness was statistically significant (t= 0.2521, p = 0.012) but gender and interaction were not. (?)

#Visualization
I visualize the interaction using the fitted variables.

```{r message=FALSE}
ggplot(health_tbl, aes(x = attractiveness, y = pregnancies, color = gender)) +
  geom_smooth(method = "lm") +
  geom_point()

#write_csv(health_tbl, "../markdown/forshiny.csv")
```

